R package qtdshift: A functional programming approach to shifted probability distributions

### 2016-08-31 docs/article.Rmd
article

---
title: 'R package qtdshift: A functional programming approach to shifted probability
  ditributions'
author: "Veronica"
date: "August 25, 2016"
output: html_document
---

@@

This paper aims to be an implementation of the methodology used by Andrea Spanò article, "R package qdist: A functional programming approach to truncated probability ditributions", which provides an alternative method for computing from truncated probability distribution using a functional programming approach. I was inspired by his work to implement the same methodology to shifted probability distributions.

@@

Why shifted distributions? Shift is a distribution trasformation used daily in many statistical fields. R does not provide a specific package for shifted distribution models, but it provides package `stats` which contains a wide set of functions for standard distribution models. I refer to: probability, density, quantile and random number generator functions, that share a stable naming convention both for the names of the functions and in the first argument of these functions. In particular:

@@

    ```{r sqnorm_example}
    x <- c(0,0.1,0.2,0.3,0.4,0.5,0.6,0.7,0.8,0.9,1)
not_shifted <- sqnorm(p = x, mean = 8, sd = 1.5)
positive_shifted <- sqnorm(p = x, mean = 8, sd = 1.5, shift = 1)
negative_shifted <- sqnorm(p = x, mean = 8, sd = 1.5, shift = -1)
    ```
    We can visualize these results by plotting them:

@@

Spano S. .  _R package qdist: A functional programming approach to truncated probability ditributions_. url

>>>>

---
title: 'R package qtdshift: A functional programming approach to shifted probability distributions'
author: "Veronica"
date: "August 25, 2016"
output: pdf_document
---

@@

Shifted distributions are used daily in many statistical fields.   
A shifted distribution is a distribution to which is added a constant, $Y = X + a$, where $X$ and $Y$ are random variables and $a$ is a constant value.

The aim of this paper is to describe an R package, `qdtshift` which generates shifted distribution models for any distribution chosen. The packege was realized using a functional programming approach and it is ispired to Andrea Spano article "R package qdist: A functional programming approach to truncated probability ditributions", which provides an alternative method for computing from truncated probability distribution using a functional programming approach.

@@

R does not provide a specific package for shifted distribution models, but it provides package `stats` which contains a wide set of functions for standard distribution models: probability, density, quantile and random number generator functions. All them share a stable naming convention both for the names of the functions and in the first argument of these functions. In particular:

@@

    ```{r sqnorm_example}
x <- (1:999)/1000
not_shifted <- sqnorm(p = x, mean = 8, sd = 1.5)
positive_shifted <- sqnorm(p = x, mean = 8, sd = 1.5, shift = 1)
negative_shifted <- sqnorm(p = x, mean = 8, sd = 1.5, shift = -1)
    ```
    We can visualize these results by plotting them:

@@

Spano A. .  _R package qdist: A functional programming approach to truncated probability ditributions_. url
